This PDF is a Git Repository\\Containing its Own \LaTeX\ Source

### 2017-04-14 article.tex
Apparently have to make the PDF minor version less than 5 to get Adobe to load it
Started on a file format figure, but that pushed the PDF over 0xFFFF bytes!

@@

\title{This PDF is a Git Repo\\Containing its Own \LaTeX\ Source}
\author{Evan Sultanik}
\date{April 11, 2017}

@@

>>>>

\pdfminorversion=4

\usepackage{tikz}
\usetikzlibrary{fit}

@@

\title{This PDF is a Git Repository\\Containing its Own \LaTeX\ Source}
\author{Evan Sultanik}
\date{April 11, 2017}

@@

The file format for Git bundles doesn't appear to be formally
specified anywhere, however, inspecting \texttt{bundle.c} reveals that
it's relatively straightforward:
\begin{center}
\begin{tikzpicture}
  \node[text width=0.9\hsize] at (0,0) (sig) {\footnotesize\texttt{\# v2 git bundle}};
  \node[inner sep=0mm,fit=(sig),draw,rounded corners,dashed,minimum width=0.9\hsize] (sigbox) {};
  \node[draw,rounded corners,fill=white] at (sigbox.north) (siglabel) {\scriptsize Git Bundle Signature};
  \node[text width=0.9\hsize,anchor=north west,yshift=-1mm] at (sig.south west) (b1) {\footnotesize\tt 3aa340a2e3d125ab6703e5c9bdfede2054a9c0c5 refs/heads/master};
  \node[text width=0.9\hsize,anchor=north west,yshift=-1mm] at (b1.south west) (b2) {\footnotesize\tt 3aa340a2e3d125ab6703e5c9bdfede2054a9c0c5 refs/remotes/origin/master};
  \node[text width=0.9\hsize,anchor=north west,yshift=-1mm] at (b2.south west) (b3) {\footnotesize\tt 4146cfe2fe9249fc14623f832587efe197ef5d2d refs/stash};
  \node[text width=0.9\hsize,anchor=north west,yshift=-1mm] at (b3.south west) (b4) {\footnotesize\tt babdda4735ef164b7023be3545860d8b0bae250a HEAD};
  \node[inner sep=0mm,fit=(b1) (b4),draw,rounded corners,dashed,minimum width=0.9\hsize] (digestbox) {};
  \node[rotate=-90,draw,rounded corners,fill=white] at (digestbox.east) {\scriptsize Digest};
\end{tikzpicture}
\end{center}
